The Talking Heads Experiment

### 2015-04-22 chap10/chap10.tex
minor: correction in small caps

Within this experimental setting three different strategies were tried in a long-term experiment where
a new strategy was injected at certain stages and performance monitored: 
\begin{itemize}
\item In stage I, agents use 
the Discrimination Game strategy and the Naming Game strategy discussed in chapters 4 and 5. A 
lexicon is emerging and there are some successful games (those for which the speaker and the hearer see the situation from 
the same perspective). But the lexicon keeps expanding and success is very limited as games where robots have a different 
perspective on the rolling ball all fail. 
\item In stage II, agents have an extended 
strategy where agents can geometrically transform a model of the scene, based on their own perspective, into a model of the scene 
as seen from the perspective of the hearer. They can then conceptualise the scene from that perspective. 
Communicative success significantly increases and the 
lexicon starts to decrease. However there is ambiguity because the hearer cannot know whether
the speaker has conceptualised the 
scene from his own viewpoint or performed a perspective reversal, leading to a large number of failed communications 
(more than 50 \%). 
\item In stage \textsc{iii}, a more elaborate stratergy is used. The speaker now expresses whether he has performed perspective 
reversal (as in `{\itshape to your} left' vs. simply `left'). Only with this strategy are agents able to reach high 
communicative success with a stable inventory. 
\end{itemize}

>>>>

Within this experimental setting three different strategies were tried in a long-term experiment where
a new strategy was injected at certain stages and performance monitored: 
\begin{itemize}
\item In stage \textsc{i}, agents use 
the Discrimination Game strategy and the Naming Game strategy discussed in chapters 4 and 5. A 
lexicon is emerging and there are some successful games (those for which the speaker and the hearer see the situation from 
the same perspective). But the lexicon keeps expanding and success is very limited as games where robots have a different 
perspective on the rolling ball all fail. 
\item In stage \textsc{ii}, agents have an extended 
strategy where agents can geometrically transform a model of the scene, based on their own perspective, into a model of the scene 
as seen from the perspective of the hearer. They can then conceptualise the scene from that perspective. 
Communicative success significantly increases and the 
lexicon starts to decrease. However there is ambiguity because the hearer cannot know whether
the speaker has conceptualised the 
scene from his own viewpoint or performed a perspective reversal, leading to a large number of failed communications 
(more than 50 \%). 
\item In stage \textsc{iii}, a more elaborate stratergy is used. The speaker now expresses whether he has performed perspective 
reversal (as in `{\itshape to your} left' vs. simply `left'). Only with this strategy are agents able to reach high 
communicative success with a stable inventory. 
\end{itemize}
